Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-09-23 prob.tex
prob.tex Start typing some interpretation... (?)

% \makeatletter
% \newtheoremstyle{indented}
%   {3pt}% space before
%   {3pt}% space after
%   {\addtolength{\@totalleftmargin}{3.5em}
%    \addtolength{\linewidth}{-3.5em}
%    \parshape 1 3.5em \linewidth}% body font
%   {}% indent
%   {\bfseries}% header font
%   {.}% punctuation
%   {.5em}% after theorem header
%   {}% header specification (empty for default)
% \makeatother
% \theoremstyle{indented}
\theoremstyle{remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{thm}{Theorem}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\pr}[2]{\langle #1, #2 \rangle}
\newcommand{\proj}[1]{|#1 \rangle\langle #1 |}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}
\newcommand{\poss}{{\mbox{\wesa{possible}}}}
\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
\newcommand{\likely}{{\mbox{\wesa{likely}}}}
\newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
\newcommand{\necess}{{\mbox{\wesa{certain}}}}
\newcommand{\overflow}{{\mbox{\wesa{overflow}}}}
\newcommand{\unknown}{{\mbox{\wesa{unknown}}}}

@@

The Bondareva-Shapley theorem can be used to algorithmically decide
non-empty core because the minimal balanced sets can be generated
by an algorithm~\cite{Peleg1965}. However, the number of minimal
balanced sets grows very rapidly with $\left|\Omega\right|$, the
size of $\Omega$~\cite{Shapley1967,Zhao2008}\footnote{\yutsung{Prove the number of minimal balanced sets grow exponentially
or more?}}, so that we have only verified every interval-valued probability
measure has a non-empty core when $\left|\Omega\right|\le5$ so far.\footnote{\yutsung{The program for $\left|\Omega\right|=6$ is running now.
It seems that it will not blow up the memory, but I still have no
idea when it will finish, and whether the result will be in our side
or not...?}}

@@

Mathematically, to fix the magnetic field of the Stern-Gerlach experiment
is to pick a orthonormal basis~$\Omega=\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$
for a given Hilbert space~$\Hilb$ of dimension~$d$, and the state
of the silver atom can be represented by a density matrix~$\rho$
written in the same basis, i.e., $\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{d}}\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{d}}r_{ij}\ket{\psi_{i}}\bra{\psi_{j}}$.
As we discussed in the last paragraph, the Born rule of the mixed
state~$\rho$ induces a classical probability measure~$\pmeas':2^{\Omega}\rightarrow[0,1]$
on $\Omega$. Let $E\in2^{\Omega}$ be a classical event and $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in E}}\proj{\psi_{j}}$
be the quantum event corresponding to subspace span by $E$, we can
have
\begin{equation}
\pmeas'\left(E\right)=\mu_{\rho}^{B}\left(P\right)\overset{\left(\ref{BornRule.mixed}\right)}{=}\Tr\left(\rho P\right)=\sideset{_{\mathbb{R}}}{_{\ket{\psi_{j}}\in E}}\sum r_{jj}\textrm{ .}\label{BornRule.mixed-1}
\end{equation}
By equation (\ref{eq:Radon-Nikodym}), the Radon-Nikodym derivative
of $\pmeas'$ is $f\left(\ket{\psi_{j}}\right)=r_{jj}$, which is
just the diagonal elements of $\rho$. In this sense, the Radon-Nikodym
derivative~$f$ is a special case of the density matrix~$\rho$,
and the Radon-Nikodym theorem is a special case of Gleason's theorem~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}.

@@

>>>>

% \makeatletter
% \newtheoremstyle{indented}
%   {3pt}% space before
%   {3pt}% space after
%   {\addtolength{\@totalleftmargin}{3.5em}
%    \addtolength{\linewidth}{-3.5em}
%    \parshape 1 3.5em \linewidth}% body font
%   {}% indent
%   {\bfseries}% header font
%   {.}% punctuation
%   {.5em}% after theorem header
%   {}% header specification (empty for default)
% \makeatother
% \theoremstyle{indented}
\theoremstyle{remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{thm}{Theorem}
\newtheorem{case}{Case}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\pr}[2]{\langle #1, #2 \rangle}
\newcommand{\proj}[1]{|#1 \rangle\langle #1 |}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}
\newcommand{\poss}{{\mbox{\wesa{possible}}}}
\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
\newcommand{\likely}{{\mbox{\wesa{likely}}}}
\newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
\newcommand{\necess}{{\mbox{\wesa{certain}}}}
\newcommand{\overflow}{{\mbox{\wesa{overflow}}}}
\newcommand{\unknown}{{\mbox{\wesa{unknown}}}}

@@

The Bondareva-Shapley theorem can be used to algorithmically decide
non-empty core because the minimal balanced sets can be generated
by an algorithm~\cite{Peleg1965}. However, the number of minimal
balanced sets grows very rapidly with $\left|\Omega\right|$, the
size of $\Omega$~\cite{Shapley1967,Zhao2008}\footnote{\yutsung{Prove the number of minimal balanced sets grow exponentially
or more?}}, so that we have only verified every interval-valued probability
measure has a non-empty core when $\left|\Omega\right|\le5$ so far.\footnote{\yutsung{The program for $\left|\Omega\right|=6$ blows up the memory
again, and the symmetric answer doesn't really work. Hence, currently
only back-track randomized program still searches IVPM with a extremely
slow speed...}}

@@

Mathematically, to fix the magnetic field of the Stern-Gerlach experiment
is to pick a orthonormal basis~$\Omega=\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$
for a given Hilbert space~$\Hilb$ of dimension~$d$, and the state
of the silver atom can be represented by a density matrix~$\rho$
written in the same basis, i.e., $\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{d}}\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{d}}r_{ij}\ket{\psi_{i}}\bra{\psi_{j}}$.
As we discussed in the last paragraph, the Born rule of the mixed
state~$\rho$ induces a classical probability measure~$\pmeas^{\Omega}:2^{\Omega}\rightarrow[0,1]$
on $\Omega$. Let $E\in2^{\Omega}$ be a classical event and $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in E}}\proj{\psi_{j}}$
be the quantum event corresponding to subspace span by $E$, we can
have
\begin{equation}
\pmeas^{\Omega}\left(E\right)=\mu_{\rho}^{B}\left(P\right)\overset{\left(\ref{BornRule.mixed}\right)}{=}\Tr\left(\rho P\right)=\sideset{_{\mathbb{R}}}{_{\ket{\psi_{j}}\in E}}\sum r_{jj}\textrm{ .}\label{BornRule.mixed-1}
\end{equation}
By equation (\ref{eq:Radon-Nikodym}), the Radon-Nikodym derivative
of $\pmeas'$ is $f\left(\ket{\psi_{j}}\right)=r_{jj}$, which is
just the diagonal elements of $\rho$. In this sense, the Radon-Nikodym
derivative~$f$ is a special case of the density matrix~$\rho$,
and the Radon-Nikodym theorem is a special case of Gleason's theorem~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}.

@@

Although theorem~\ref{thm:Shapley} and \ref{def:EmptyCoreQuantumInterval-valuedProbability}
gives opposite results, their results are consistent. If we pick a
orthonormal basis~$\Omega=\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$,
let $E\in2^{\Omega}$ be a classical event and $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in E}}\proj{\psi_{j}}$
be the quantum event corresponding to subspace span by $E$, we can
define a classical interval-valued probability measure$\bar{\mu}^{\Omega}\left(E\right)=\bar{\mu}\left(P\right)$.
There are two cases.

\begin{case}If $\ket{\psi_{1}}$ is either $\ket{0}$, $\ket{\ps}$,
or $\ket{\ps'}$, then we have

\[
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\bar{\mu}^{\Omega}(\emptyset) & = & \imposs\\
\bar{\mu}^{\Omega}(\{\ket{\psi_{1}}\}) & = & \imposs\\
\bar{\mu}^{\Omega}(\{\ket{\psi_{2}}\}) & = & \unknown\\
\bar{\mu}^{\Omega}(\{\ket{\psi_{3}}\}) & = & \unknown
\end{array} & \begin{array}{rcl}
\bar{\mu}^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}}\}) & = & \unknown\\
\bar{\mu}^{\Omega}(\{\ket{\psi_{3}},\ket{\psi_{1}}\}) & = & \unknown\\
\bar{\mu}^{\Omega}(\{\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & \necess\\
\bar{\mu}^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & \necess
\end{array}\end{array}
\]
It is easy to verify that $\bar{\mu}^{\Omega}$ has an non-empty core,
and $\pmeas^{\Omega}:2^{\Omega}\rightarrow\left[0,1\right]$ is in
its core. 
\[
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\pmeas^{\Omega}(\emptyset) & = & 0\\
\pmeas^{\Omega}(\{\ket{\psi_{1}}\}) & = & 0\\
\pmeas^{\Omega}(\{\ket{\psi_{2}}\}) & = & 1/2\\
\pmeas^{\Omega}(\{\ket{\psi_{3}}\}) & = & 1/2
\end{array} & \begin{array}{rcl}
\pmeas^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}}\}) & = & 1/2\\
\pmeas^{\Omega}(\{\ket{\psi_{3}},\ket{\psi_{1}}\}) & = & 1/2\\
\pmeas^{\Omega}(\{\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & 1\\
\pmeas^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & 1
\end{array}\end{array}
\]
\qed\end{case}

\begin{case}If neither $\ket{0}$, $\ket{\ps}$, nor $\ket{\ps'}$
is in $\Omega$, then we have

\[
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\bar{\mu}^{\Omega}(\emptyset) & = & \imposs\\
\bar{\mu}^{\Omega}(\{\ket{\psi_{1}}\}) & = & \unknown\\
\bar{\mu}^{\Omega}(\{\ket{\psi_{2}}\}) & = & \unknown\\
\bar{\mu}^{\Omega}(\{\ket{\psi_{3}}\}) & = & \unknown
\end{array} & \begin{array}{rcl}
\bar{\mu}^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}}\}) & = & \unknown\\
\bar{\mu}^{\Omega}(\{\ket{\psi_{3}},\ket{\psi_{1}}\}) & = & \unknown\\
\bar{\mu}^{\Omega}(\{\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & \unknown\\
\bar{\mu}^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & \necess
\end{array}\end{array}
\]
In this case, $\pmeas^{\Omega}:2^{\Omega}\rightarrow\left[0,1\right]$
defined by the following is in the core of $\bar{\mu}^{\Omega}$.
\[
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\pmeas^{\Omega}(\emptyset) & = & 0\\
\pmeas^{\Omega}(\{\ket{\psi_{1}}\}) & = & 1/3\\
\pmeas^{\Omega}(\{\ket{\psi_{2}}\}) & = & 1/3\\
\pmeas^{\Omega}(\{\ket{\psi_{3}}\}) & = & 1/3
\end{array} & \begin{array}{rcl}
\pmeas^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}}\}) & = & 1/3\\
\pmeas^{\Omega}(\{\ket{\psi_{3}},\ket{\psi_{1}}\}) & = & 1/3\\
\pmeas^{\Omega}(\{\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & 1/3\\
\pmeas^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & 1
\end{array}\end{array}
\]
\qed\end{case}
